---
title: "p8105_hw6_bes2161.Rmd"
author: "Brittany Shea"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(viridis)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

### Problem 1

# Load and clean data:

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

# Produce estimates of two quantities using bootstrap sample:

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

The $\hat{r}^2$ value is high, the lower bound at 1 could be an issue, and the shape is not symmetric.

# Plot distribution:

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

The distribution is a bit skewed. It also includes some outliers. 

### Problem 2

# Load and clean data:

```{r}
wp = read_csv("data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate_if(is.character, str_to_lower) %>% 
  unite("city_state", city:state, sep = ", ") %>% 
  mutate(reported_date = lubridate::ymd(reported_date)) %>% 
  mutate(
    solved = as.numeric(disposition == "closed by arrest"),
    victim_age = as.numeric(victim_age)) %>% 
  filter(victim_race == "white" | victim_race == "black", city_state != "dallas, tx" & city_state != "phoenix, az" & city_state != "kansas city, mo" & city_state != "tulsa, al")
```

# Create Baltimore dataframe:

```{r}
baltimore_df = wp %>% 
  filter(city_state == "baltimore, md") %>%
  select(solved, victim_age, victim_race, victim_sex)
```

# Fit logistic regression model for Baltimore using `glm`:

```{r}
balt_fit_logistic = 
  baltimore_df %>% 
  glm(solved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 
```

# Tidy data and obtain the estimate and confidence interval of the adjusted odds ratio:

```{r}
balt_fit_logistic %>%  
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
    ci_lower = quantile(OR, 0.025), 
    ci_upper = quantile(OR, 0.975)) %>% 
  select(term, OR, ci_lower, ci_upper) %>% 
  filter(term == "victim_sexmale") %>% 
  knitr::kable(digits = 3)
```

# Define function:

```{r}
fun <- function(df) {
    glm(
        formula = solved ~ victim_age + victim_race + victim_sex
        , data = df
        , family = binomial
    ) %>%
    
    broom::tidy() %>%
    mutate(OR = exp(estimate),
    ci_lower = quantile(OR, 0.025), 
    ci_upper = quantile(OR, 0.975)) %>% 
    select(term, OR, ci_lower, ci_upper)
}
```

# Run `glm` for each of the cities:

```{r}
all_fit = wp %>% 
  nest(data = -city_state) %>% 
  mutate(results = map(data, fun)) %>% 
  unnest(results) %>% 
  filter(term == "victim_sexmale")
```

# Create a plot:

```{r}
all_fit %>% 
  mutate(
    OR = str_c("n = ", OR),
    OR = fct_inorder(OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point()

all_fit %>% 
  mutate(
    OR = str_c("n = ", OR),
    OR = fct_inorder(OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

```

This plot shows that New York, NY has the smallest OR, while Albuquerque, NM has the highest OR for solving homicides for male victims compared to female victims.

### Problem 3

# Load and clean data:

```{r}
bw = read_csv("data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = as.factor(babysex),
    babysex = fct_recode(babysex, "male" = "1", "female" = "2"),
    frace = as.factor(frace),
    frace = fct_recode(frace, "white" = "1", "black" = "2", "asian" = "3", 
                       "puerto rican" = "4", "other" = "8"),
    malform = as.logical(malform),
    mrace = as.factor(mrace),
    mrace = fct_recode(mrace, "white" = "1", "black" = "2", "asian" = "3", 
                       "puerto rican" = "4")) %>% 
  select(-pnumlbw, -pnumsga)
```

# Select variables of interest:

```{r}
bw_fit = bw %>% 
  select(bwt, blength, smoken, momage, ppbmi)
```

I selected these variables because I was interested in seeing if certain variables related to mother's health, such as average number of cigarettes smoked per day during pregnancy, are associated with baby's birth weight. I also included baby's length at birth to compare with the other two models. I used a linear fit for this model using `lm`.

# Propose first regression model for birth weight:

```{r}
fit1 = lm(bwt ~ blength + smoken + momage + ppbmi, data = bw_fit)
```

# Plot first model: 

```{r}
bw %>% 
  modelr::add_residuals(fit1) %>% 
  modelr::add_predictions(fit1) %>% 
  mutate(fitted_prob = boot::inv.logit(pred)) %>% 
  ggplot(aes(x = fitted_prob, y = resid)) + geom_violin()
```

# Fit two additional models: 

```{r}
fit2 = lm(bwt ~ blength + gaweeks, data = bw)

fit3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = bw)
```

# Plot three models to get idea of goodness of fit:

```{r}
bw %>% 
  gather_predictions(fit1, fit2, fit3) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = blength, y = bwt)) +
  geom_point(alpha = .5) +
  geom_line(aes(y = pred), color = "red") +
  facet_grid(~model)
```

# Check prediction errors; use `crossv_mc` to perform training/testing split.

```{r}
bw = 
  crossv_mc(bw, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

# Fit models to training data and get RMSEs for the testing data:

```{r}
bw = 
  bw %>% 
  mutate(
    fit1 = map(train, ~lm(bwt ~ blength + smoken + momage + ppbmi, data = .x)),
    fit2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    fit3 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))) %>%
  mutate(
    rmse_fit1 = map2_dbl(fit1, test, ~rmse(model = .x, data = .y)),
    rmse_fit2 = map2_dbl(fit2, test, ~rmse(model = .x, data = .y)),
    rmse_fit3 = map2_dbl(fit3, test, ~rmse(model = .x, data = .y)))
```

# Plot prediction error distribution for each candidate model:

```{r}
bw %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

By comparing the cross-validated prediction error of the three models, it appears that the third model, fit3, is a better fit than the other two models. This is the model that included all interactions, including the three-way interaction. It included head circumference, length, and sex.
